Ensemble Methods for Robust Feature Selection

### 2016-08-02 paper/paper.tex
comparison of methods

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.07\textwidth]{images/Accuracy_of_the_different_combinations.pdf}
  \caption{Accuracy}
  \label{fig:combination_accuracy}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.07\textwidth]{images/Robustness_of_the_different_combinations.pdf}
  \caption{Robustness}
  \label{fig:combination_robustness}
\end{subfigure}
\caption{Different combination of feature selectors (RLF and LSO corresponds respectively to RELIEFF and Lasso)}
\label{fig:combination_results}
\end{figure}

>>>>

The methods were also compared with regards to their performance and robustness on the different combinations. However, as can be seen in figure \ref{fig:methods_results} the methods do not seems to have a great impact on the results. Therefore the choice of the combined feature selectors appears to be more important than the methods used to combine them.

\begin{figure}[!t]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.07\textwidth]{images/Accuracy_of_the_different_combinations.pdf}
  \caption{Accuracy}
  \label{fig:combination_accuracy}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.07\textwidth]{images/Robustness_of_the_different_combinations.pdf}
  \caption{Robustness}
  \label{fig:combination_robustness}
\end{subfigure}
\caption{Results for the different combination of feature selectors. RLF and LSO corresponds respectively to RELIEFF and Lasso.}
\label{fig:combination_results}
\end{figure}

\begin{figure}[!t]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.07\textwidth]{images/Accuracy_of_the_different_methods.pdf}
  \caption{Accuracy}
  \label{fig:methods_accuracy}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.07\textwidth]{images/Robustness_of_the_different_methods.pdf}
  \caption{Robustness}
  \label{fig:methods_robustness}
\end{subfigure}
\caption{Results for the different methods on average on the different combinations. "Average +" is the average method with the normalized sum. When "\& Perf." is indicated the performance was also used to aggregate the weights.}
\label{fig:methods_results}
\end{figure}
